\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-09 stlc-linkTran-typing.tex
Finishing Linkage Transformer example.

Our final target is to construct a term $\goodInh{\cdot}{?}{\lsig_5}{\lsig_5'}$ using the four constructors. There are two upcasting operations required $\goodTerm{A_3'}{\uparrow s_3}{A_3}$ and $\goodTerm{A_4'}{\uparrow s_4}{A_4}$ (omitting debruijn indices here) for checking the compatibility between $A_i$ and $A_i'$.

>>>>

Our final target is to construct a term $\goodInh{\cdot}{?}{\lsig_5}{\lsig_5'}$ using the four linkage transformers' rules. There are two upcasting operations $\goodTerm{A_3'}{\uparrow s_3}{A_3}$ and $\goodTerm{A_4'}{\uparrow s_4}{A_4}$ (omitting debruijn indices here) for checking the compatibility between $A_i$ and $A_i'$.
